Calculating Module Enrichment and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-10 jss/article.tex
[skip ci] update gbm.

>>>>

\begin{verbatim}
library(RNaviCell)

n <- NaviCell()

n$proxy_url <- "https://acsn.curie.fr/cgi-bin/nv_proxy.php"
n$map_url <- "https://acsn.curie.fr/navicell/maps/acsn/master/index.php"

n$launchBrowser()

mat <- n$readDatatable('gbm.txt')
n$importDatatable("Mutation data", "GBM", mat)

n$drawingConfigSelectGlyph(1, TRUE)

n$glyphEditorOpen(1)
n$glyphEditorSelectSample(1, "categ")
n$glyphEditorSelectShapeDatatable(1, "GBM")
n$glyphEditorSelectColorDatatable(1, "GBM")
n$glyphEditorSelectSizeDatatable(1, "GBM")
n$glyphEditorApply(1)

n$unorderedConfigSetDiscreteShape("GBM", "sample", 0, 1)
n$unorderedConfigSetDiscreteShape("GBM", "sample", 1, 5)
n$unorderedConfigApply("GBM", "shape")

n$unorderedConfigSetDiscreteColor("GBM", "sample", 0, "398BC3")
n$unorderedConfigSetDiscreteColor("GBM", "sample", 1, "CC5746")
n$unorderedConfigApply("GBM", "color")

n$unorderedConfigSetDiscreteSize("GBM", "sample", 0, 4)
n$unorderedConfigSetDiscreteSize("GBM", "sample", 1, 14)
n$unorderedConfigApply("GBM", "size")
